---
title: "Project for Developing Data Products"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Purpose of Application
The application is to be used to create scatterplot of 'Petal Length' to 'Sepal Length' for selected 'Species' in the Iris dataset.

```{r}
plot(0, type = "n", xlab = "Sepal Length", ylab = "Petal Length", xlim = c(0, 10), ylim =  c(0, 10))
```

## Input and Outputs of Application
The application has checkboxes for the 3 species in the Iris dataset:  
- Plot Setosa  
- Plot Versicolor  
- Plot Virginica  

The output would be a scatterplot of the petal length against sepal length for the selected species.

Different species will be plotted with dots of different colors.

## Example Plot with Setosa and Virginica
```{r}
data <- iris[which(iris$Species == "setosa" | iris$Species == "virginica"), ]
plot(data$Sepal.Length, data$Petal.Length, col = data$Species, xlab = "Sepal Length", ylab = "Petal Length")
```

## Thank you
Thank you! Hope you will like my application!